Fig3

### 2020-05-07 analysis/figure-3.Rmd
better fig 3, now with 3 correlation matreces

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", " ") + theme(axis.text.x = element_text())

@@

# most sig DEGs

c1 <-  plottopDEGs(envDEGs, "female", "#3A80B9", "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
c2 <-  plottopDEGs(PRLDEGs, "male", "#3A80B9", "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
c3 <-  plottopDEGs(PRLDEGs, "female", "#19757A", "LFC lo vs. hi PRL", NULL)
c4 <-  plottopDEGs(PRLDEGs, "male", "#19757A", "LFC lo vs. hi PRL", NULL)

b <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))

c <- plot_grid(c1,c2,c3,c4, align = "v" , rel_heights = c(1.2,1))

bc <- plot_grid(b,c, labels = c("B","C"), label_size = 8, rel_widths = c(1.2,1))

d1 <-plotcorrplot(piteggchick, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 eggs vs. chicks DEGs")
d2 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 lo vs. PRL DEGs")
d3 <-plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes from WGCNA module with PRL")

d <- plot_grid(d1,d2,d3, nrow = 1, align = "h", labels = c("D"), label_size = 8)

fig3 <- plot_grid(a, bc, d, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3

#pdf(file="../figures/fig3.pdf", width=7.25, height=7.25)
#plot(fig3)
#dev.off()
```

>>>>

a1 <- plotpc12(pca1, pca2, pca1$treatment, allcolors, "Pituitary gene expression", " ")   
a2 <- plotprolactin(PRLpit, PRLpit$counts, "PRL", " ") + theme(axis.text.x = element_text())  +
  theme(legend.position = c(0.8,0.2)) + guides(fill = FALSE)

@@

b6 <-  plottopDEGs(envDEGs, "female", "#3A80B9", "LFC eggs vs. chicks", "Top 10 female DEGs") + labs(title = " ")
b7 <-  plottopDEGs(PRLDEGs, "male", "#3A80B9", "LFC eggs vs. chicks", "Top 10 male DEGs") + labs(title = " ")
b8 <-  plottopDEGs(PRLDEGs, "female", "#19757A", "LFC lo vs. hi PRL", NULL)
b9 <-  plottopDEGs(PRLDEGs, "male", "#19757A", "LFC lo vs. hi PRL", NULL)

b15 <- plot_grid(b1,b25,nrow = 1, rel_widths = c(1.2,1))
b69 <- plot_grid(b6,b7,b8,b9, align = "v" , rel_heights = c(1.2,1))
b <- plot_grid(b15,b69, labels = c("B"), label_size = 8, rel_widths = c(1.2,1))

c1 <- plotcorrplot(piteggchick, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 eggs vs. chicks DEGs")
c2 <- plotcorrplot(pithilo, NULL) + theme(legend.position = "none") + labs(subtitle = "Top 20 lo vs. PRL DEGs") 
d <- plotcorrplot(pitWGCNA, NULL) + theme(legend.position = "none") + labs(subtitle = "20 genes from WGCNA module with PRL") + theme(legend.position = "right")

cd <- plot_grid(c1,c2,d, nrow = 1, align = "h", labels = c("C", "", "D"), label_size = 8, rel_widths = c(1,1,1.3))

fig3 <- plot_grid(a, b, cd, nrow = 3, rel_heights = c(1.2,2,1.8))
fig3

pdf(file="../figures/fig3-1.pdf", width=7.25, height=7.25)
plot(fig3)
dev.off()
```
